### 2022-08-23 LaTeX/Vorlage Latex - Eng.tex
Working on Latex and MSGARC R file.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% List of Acronyms %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{List of Acronyms} %Bitte alphabetisch ordnen!
\addcontentsline{toc}{section}{Abbreviation directory}
\rule[0pt]{0mm}{10pt}
\noindent Include an abbreviation directory if you use more than three uncommon abbreviations.\\

\begin{tabular}{l l l}

	% B
	BLL && Bayesian Local Likelihood\\
	BR&&Bounded Rationality\\
	% D
	DSGE&&Dynamic Stochastic General Equilibrium\\

\end{tabular}

@@

We test 3 models: 
1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
2. A markov-switching model without indicators
3. A markov-switching model with indicators

@@

\section{HMM with time-varying transition probabilities}
Our goal is to maximize the incomplete data log-likelihood $\log f(y \mid X ; \theta)=\log \sum_{s_{1}=1}^{2} \sum_{s_{2}=1}^{2} \ldots \sum_{s_{T}=1}^{2} f(y, s \mid X ; \theta)$ which is not feasible to compute (complexity). \\
Hence we maximize the expected value of the complete data log-likelihood $\log f(y, s \mid X ; \theta)$. Let $Y_t$ be the natural filtration of $Y$ and $\mathbb{X}_t$.
\section{First chapter of main text}

Divide your text into chapters (1; 2; 3; ...), sections (1.1; 1.2; 1.3; ...) and subsections (2.1.1; 2.1.2; 2.1.3; ...). A bullet point 2.1.1 is nonsensical unless a bullet point 2.1.2 follows. Give all chapters, sections, and subsections expressive headings.
\newpage

\subsection{First section of first chapter of main text}
This section is nonsensical unless a section 2.2 follows.

\subsubsection{First subsection}
This subsection is nonsensical unless a section 2.1.2 follows. You may include a table in this section. Label the table and indicate the source including the page number like you would in the continuous text. The contents of the table below are taken from the highly cited Smets \& Wouters (2007: 597).
\begin{table}[H]
	\centering
	\resizebox{\textwidth}{!}{%
		\begin{tabular}{cccccccccccccc}
			\hline \hline
			&&&&&&&&&&&&&\\
			&	Base& & $\xi_p=0.1$ & &$\xi_w=0.1$ & & $\iota_p\approx0.0$&& $\iota_w\approx0.0$ &&$\phi=0.1$ && $\lambda=0.1$ \\
			\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} 
			\textit{Est. Mode}&&&&&&&&&&&&&\\
			$\varphi$ & 5.48&& 4.41 && 2.78 && 5.45 &&5.62 && 0.1 && 1.26\\
			$\sigma_c$& 1.39 && 1.31 && 1.80 && 1.43 && 1.42 && 2.78&& 2.90\\
			$\sigma_l$&1.92&&1.48&&0.25&&1.91&&1.91&&5.24&&1.21\\
			$\lambda$&0.71 && 0.70 && 0.34 && 0.70&& 0.71&& 0.12 && 0.10\\
			$\xi_w$&0.73&& 0.55&&0.10&&0.75&&0.75&&0.89&&0.73\\
			$\xi_p$&0.65&&0.10&&0.48&&0.66&&0.69&&0.86&&0.62\\
			$\iota_p$&0.22&&0.84&&0.24&&0.01&&0.24&&0.08&&0.21\\
			$\iota_w$&0.59&&0.71&&0.68&&0.61&&0.01&&0.39&&0.61\\
			$r_\pi$&2.03&&2.15&&2.15&&2.01&&2.01&&2.03&&2.24\\
			$r_y$&0.08&&0.08&&0.08&&0.08&&0.09&&0.23&&0.12\\
			$r_{\Delta y}$&0.22&&0.21&&0.25&&0.22&&0.22&&0.30&&0.29\\
			&&&&&&&&&&&&&\\
			\textit{Marg. LH} & && && && && && &&\\
			&-923&&-975&&-973&&-918&&-927&&-1084&&-959\\
			&&&&&&&&&&&&&\\
			\hline \hline
	\end{tabular}}
	\caption[Example table (short description)]{An example table. Describe it shortly. Source: Smets \& Wouters (2007): 597.}
\end{table}
\newpage
 \subsubsection{Second Subsection}
You may want to include a figure here. Label the figure and include the source. You may also want to include a second figure that you created yourself.
 \begin{figure}[H]
 	\includegraphics[width=\textwidth]{example_figure}
 	\caption[Short description]{IRFs. SW baseline model with standard calibration (black line, appendix table 8), with low habits in consumption (blue line, table 1) and with low capital adjustment cost (blue line, table 1). Source: Own simulation.}
 \end{figure}
\newpage
\subsection{Second section of first chapter of main text}
This section follows section 2.1 with its subsections. Make it clear how sec-tions and chapters in your work link together. Some introductory and guiding sentences may help the reader and yourself not to lose track of the line of reasoning.

@@

\section{Second chapter of main text}

The main text can consist of several chapters, sections and subsections.\\
Use paragraphs to divide the body text within the (sub) chapters into mean-ingful sections. Paragraphs that are longer than one page are usually too long. The reader will not remember upon reaching the end of the paragraph what the main message was. On the other hand, a paragraph that consists of only one sentence is likely too short.\\
If you include illustrations, tables and / or equations in the text, explain them to the reader and describe the results in the text. When using symbols in the text, include their meaning (for example, the money stock M).

@@

\section{Conclusion}
End your work with a chapter in which you summarize your findings, formulate some theses, or point out unsolved problems.\\
Before submitting your work, check the following (non-exhaustive) checklist to see if you have met the basic requirements of a well-crafted seminar pa-per, bachelor or master thesis.
\begin{itemize}
	\item Does the text still contain spelling or punctuation errors?
	\item Do you use a fluent and understandable way of expression?
	\item Are words, passages or entire pages missing?
	\item Does the table of contents (and other directories) match the structure of the text and page numbers?
	\item Is the bibliography complete? (Delete bibliography entries that you do not cite!)
	\item Are all references to literature, figures and appendix correct? Did you forget any references?
	\item Is the layout (headings, text formatting, etc.) clear and consistent?
	\item Did you include all necessary components of a scientific paper?
	\item Did you correctly number figures, tables, footnotes, equation?

\end{itemize}
\newpage

\newpage
\addcontentsline{toc}{section}{Bibliography}
\section*{Bibliography}
In the bibliography, you list all the sources that you use and therefore cite in the text (sources that you have read but not cited should not be listed). Sort the entries in the bibliography, listed according to a consistent style, alphabetically by last name.
\begin{itemize}
	\item[] Adolfson, M.; Las\'een, S.; Lind\'e, J. (2007): Bayesian Estimation of an Open Economy DSGE Model with Incomplete Pass-Through, \textit{Journal of International Economics} 72 (2): 481-511.
 \item[] Christiano, L.; Eichenbaum, M.; Evans, C. (2005): Nominal Rigidities and the Dynamic Effects of a Shock to Monetary Policy, \textit{Journal of Political Economy} 113 (1): 1-45.
 \item[] Hommes, C.; Makarewicz, T.; Massaro, D.; Smits, T. (2017): Genetic Algorithm Learning in a New Keynesian Macroeconomic Setup, \textit{Journal of Evolutionary Economics} 27: 1133-1155.
	\item[] Smets, F.; Wouters, R. (2007): Shocks and Frictions in US Business Cycles: A Bayesian DSGE Approach, \textit{The American Economic Review} 97: 
	\item[] Wieland, V.; Wolters, M. (2012): Forecasting and Policy Making, \textit{IMFS Working Paper Series} No. 62.
\end{itemize}

\addcontentsline{toc}{section}{Appendix}
\begin{appendix}
	The appendix contains tables, data, questionnaires, proofs, derivations, etc., which you consider merely additional information and negatively affect the reading flow in the main text. Do not use the appendix for outsourcing text that does not fit into the main text due to page restrictions. Only include an appendix when needed.
	\section{Equality of 1 and 2}
	\label{proof:1equal2}
	\begin{align}
	x^2 &= x^2 \\
	x^2 - x^2 &= x^2 - x^2 \\
	x^2 - x^2 &= x^2 - x^2 + x^2 - x^2	\\
	x\cdot\left(x-x\right) &= \left(x+x\right)\cdot\left(x-x\right)	\\
	x &= \left(x+x\right)	\\
	1 &= 2	\hspace{1cm} q.e.d.
	\end{align}
\section{Latex examples}
\begin{table}
	\centering\rotatebox{90}{%
		\resizebox{\textheight}{!}{%
			\begin{tabular}{lccccccccccccccccccc}
				\hline \hline
				&&&&&&&&&&&&&&&&&&&\\
				\textit{Correlation}&	Animal Spirits & & Output $y_t$ & &Consumption $c_t$ & & Investment $i_t$&& Hours Worked $l_t$ &&Capital Arbitrage $q_t$ && Inflation $\pi_t$&& Rental Rate $r^k_t$&&Wage $w_t$&&Interest Rate $r_t$\\
				\cline{2-2} \cline{4-4} \cline{6-6} \cline{8-8} \cline{10-10} \cline{12-12} \cline{14-14} \cline{16-16} \cline{18-18} \cline{20-20} 
				&&&&&&&&&&&&&&&&&&&\\
				Animal Spirits&1&&-&&-0.6520**&&0.6831**&&0.3197**&&0.3259**&&0.3918**&&-0.4220&&0.1646&&-\\
				Output $y_t$&-&&1&&0.8265**&&0.4859**&&0.8559**&&0.7169**&&-0.6618**&&0.8279**&&0.4404**&&-0.5713**\\
				Consumption $c_t$&-0.6520**&&0.8265**&&1&&0.5300**&&0.6896**&&0.9628**&&-0.7739**&&0.6663**&&0.3654**&&-0.7699**\\
				Investment $i_t$&0.6831**&&0.4854**&&0.5300**&&1&&0.4229**&&0.4724**&&-0.2134*&&0.2835**&&0.1891**&&-0.2100*\\
				Hours Worked $l_t$&0.3197**&&0.8559**&&0.6896**&&0.4229**&&1&&0.5279**&&-0.4433**&&0.8108**&&0.2382*&&-0.3638**\\
				Capital Arbitrage $q_t$&0.3259**&&0.7169**&&0.9628**&&0.4724**&&0.5279**&&1&&-0.7767**&&0.5515**&&0.3607**&&-0.7936**\\
				Inflation $\pi_t$&0.3918**&&-0.6618**&&-0.7739**&&-0.2134*&&-0.4433**&&-0.7767**&&1&&-0.5601**&&-0.4131**&&0.9647**\\
				Rental Rate $r^k_t$&-0.4220&&0.8279**&&0.6663**&&0.2835**&&0.8108**&&0.5515**&&-0.5601**&&1&&0.7393**&&-0.4796**\\
				Wage $w_t$&0.1646&&0.4404**&&0.3654**&&0.1891**&&0.2382*&&0.3607**&&-0.4131**&&0.7393**&&1&&-0.3712**\\
				Interest Rate $r_t$&-&&-0.5713**&&-0.7699**&&-0.2100*&&-0.3638**&&-0.7936**&&0.9647**&&-0.4796**&&-0.3712**&&1\\
				&&&&&&&&&&&&&&&&&&&\\
				\hline \hline
	\end{tabular}}}
	\caption[Rotated table]{Rotated table. \\ **: 99\% Confidence; *: 95\% Confidence.}
\end{table}
Some aligned equations
	\begin{align}
	\widetilde{\text{E}}_tv_{t+1}&= \underbrace{(\omega_t^{v,sta}+\omega_t^{v,anc}(\varOmega+\varUpsilon(1-\varpi)))}_{\Lambda^v_t}v_{t-1} \notag \\&-\omega_t^{v,anc}\varOmega v_{t-2}+\underbrace{\omega_t^{v,anc}(1-\varpi)(1-\varUpsilon)}_{\Theta^v_t}\widetilde{\text{E}}^{anc}_{t-1}v_{t}+\omega_t^{v,anc}\varpi v^{avg.}_{t-1}
	\end{align}
	and matrices that have no tag 
	\begin{align}
	\textbf{A}_{10\times10}= \begin{pmatrix}
	A_{1,5\times5} & A_{2,5\times5} \\
	A_{3,5\times5} & A_{4,5\times5}
	\end{pmatrix}, \quad \widetilde{\textbf{B}}_{t,10\times10}= \begin{pmatrix}
	B_{1,5\times5} & B_{2,5\times5} \\
	B_{3,5\times5} & B_{4,5\times5}
	\end{pmatrix}\notag \\ \widetilde{\textbf{C}}_{t,10\times10}=\begin{pmatrix}
	C_{1,5\times5} & C_{2,5\times5} \\
	C_{3,5\times5} & C_{4,5\times5}
	\end{pmatrix}, \quad \textbf{D}_{t,10\times9}= \begin{pmatrix}
	D_{1,5\times5} & D_{2,5\times4} \\
	D_{3,5\times5} & D_{4,5\times4}
	\end{pmatrix}\notag \\
	\widetilde{\textbf{F}}_{t,10\times10}=\begin{pmatrix}
	F_{1,5\times5} & F_{2,5\times5} \\
	F_{3,5\times5} & F_{4,5\times5}
	\end{pmatrix}, \quad 	\widetilde{\textbf{G}}_{t,10\times10}= \begin{pmatrix}
	G_{1,5\times5} & G_{2,5\times5} \\
	G_{3,5\times5} & G_{4,5\times5}
	\end{pmatrix}\notag 
	\end{align}
	of the system 
   \begin{align}
   \textbf{V}_t &= \textbf{A}^{-1}\left[\widetilde{\textbf{B}}_t\textbf{V}_{t-1}+\widetilde{\textbf{C}}_t\textbf{V}_{t-2}+\widetilde{\textbf{F}}_t\widetilde{\text{E}}^{anc}_{t-1}\widetilde{\textbf{V}}_{t}+\widetilde{\textbf{G}}_t\textbf{V}^{avg.}_{t-1}+\textbf{D}\textbf{e}_t\right],
   \end{align}
	\section{Questionaire}
	Here you can include a questionnaire that you used in your paper.
\end{appendix}
\section*{Affirmation}
I hereby declare that I have composed my Bachelor/Master's thesis / Seminar paper 
\textit{"title"} independently using only those resources mentioned, 
and that I have as such identified all passages which I have 
taken from publications verbatim or in substance. I agree that the work will be reviewed using plagiarism testing software.
Neither 
this paper, nor any extract of it, has been previously 
submitted to an examining authority, in this or a similar 
form.\\ \\
\textit{Only for Bacherlor’s and Master’s theses with included CD:}\\
I have ensured that the written version of this thesis is 
identical to the version saved on the enclosed storage 
medium. \\\\\\

>>>>

% MAKE subsubsubsection possible
\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
%

@@

@@

@@

Our goal is to maximize the incomplete data log-likelihood 
$$\log f(y \mid X ; \theta)=\log \sum_{s_{1}=1}^{2} \sum_{s_{2}=1}^{2} \ldots \sum_{s_{T}=1}^{2} f(y, s \mid X ; \theta)$$ which is not feasible to compute (complexity).

\subsection{Markov-Switching Models}

\subsubsection{Exogeneous Variables}
\paragraph{Time-varying transition probabilities}
Most HMMs are trained based on an purely endogeneous variables. One way to introduce exogeneous variables X into the HMM is by using them to estimate time-varying transition probabilities. This concept has been introduced by Diebold et al. \cite{diebold_regime_1993} together with closed form solutions for Gaussian state probability distributions. Since the complexity of calculating the expected likelihood for the EM algorithm in this setting is squared in the number of observations, maximizing it numerically with respect to the parameters is computationally not feasible. Since no closed form solutions to the maximization step for any fat-tailed distributions are available in this setting, this is currently not suited to model financial market data.

\paragraph{State-space model/ DFM-MSs}
Another way to integrate outside information is to use state space models. In this setting the state is represented by one or more so called dynamic factors whose behaviour is specified in the state equation and its relation to the variable of interest in the output equation. The usefulness of this approach depends on two factors: the dynamic factor has to be somewhat predictable and 
needs to explain the output variable reasonably well. The state space model can be learned using the Kalman filters in Gaussian settings or using MCMC methods otherwise.

\subsection{Financial Market Data}

\subsubsection{Stylized Facts about returns and volatility}
Volatility is standard deviation of the log returns.
Fat-tailed. Power-law. Daily vs Monthly frequencies.

\subsubsection{GARCH}
GARCH (General Autoregressive Conditional Heteroskedasticity) has been popular in order to forecast the volatility of indices. It tries to explain the observation that the volatility of an asset tends to cluster, i.e. periods with high volatility are followed by periods with high volatility.
however the model fails to explain many phenomena which are observed, like the fat-tailedness of drawdown periods and depths (cite Robert Frey).
The general Markov-switching GARCH specification we use follows \cite{ardia_markov-switching_2019}: 
$$y_{l} \mid\left(s_{l}=k, \mathcal{I}_{l-1}\right) \sim \mathcal{D}\left(0, h_{k, t}, \xi_{k}\right)$$
$\mathcal{D}$ being some zero-mean distribution, the variance h and shape parameters $\xi$. For short time-periods the zero-mean specification is justified most of the time.  $s_t$ is the state at time t is modeled by a Markov chain.\\

A GARCH(1,1) model has the form $h_{k, t} \equiv \alpha_{0, k}+\alpha_{1, k} y_{t-1}^{2}+\beta_{k} h_{k, t-1}$. Similar to an ARMA model which tries specify the conditional mean, the GARCH model tries to specify the conditional variance. The lagged squared return term can be interpreted as a proxy for the realized variance in the last observation period. 
Long periods of high variance can be modeled by increasing the intercept $\beta$.\\

Many extensions of the GARCH model exist, like (todo). The TGARCH e.g. tries to incorporate the observation that variance caused by positive returns don't have the same effect as variance that is caused by negative returns.
$$h_{k, t}^{1 / 2} \equiv \alpha_{0, k}+\left(\alpha_{1, k} \mathbb{I}\left\{y_{t-1} \geq 0\right\}-\alpha_{2, k} \mathbb{I}\left\{y_{t-1}<0\right\}\right) y_{t-1}+\beta_{k} h_{k, t-1}^{1 / 2}$$

\section{First chapter of main text}
We try to predict S\&P index using

\subsection{Experiment description}
We compare the performance of 3 models: 
1. A naive forecast, i.e. we estimate a model/ density which assumes i.i.d. observations. 
2. A markov-switching model without indicators
3. A markov-switching model with indicators

\subsection{Data set}

\subsection{Results}

\section{Conclusion}

@@

\newpage
\addcontentsline{toc}{section}{Bibliography}
\section*{Bibliography}
In the bibliography, you list all the sources that you use and therefore cite in the text (sources that you have read but not cited should not be listed). Sort the entries in the bibliography, listed according to a consistent style, alphabetically by last name.

\bibliography{References}
\bibliographystyle{Alpha}

@@
